% -*- coding: utf-8; -*-

\documentclass[
  phd,
  %% master
  brazilian
  %%american
]{ThesisPUC}


%%%
%%% Additional Packages
%%%

%%  \usepackage[brazilian]{babel}      %% in ThesisPUC.cls
  %% \usepackage[utf8]{inputenc}        %% .
  %% \usepackage[T1]{fontenc}           %% .
  %% \usepackage{lmodern}               %% .
  %% \usepackage[pdftex]{graphicx}	%% .

  \usepackage{tabularx}
  \usepackage{multirow}
  \usepackage{multicol}
  \usepackage{colortbl}
  \usepackage[%
    dvipsnames,
    svgnames,
    x11names,
    fixpdftex
  ]{xcolor}
  \usepackage{numprint}
  \usepackage{textcomp}
  \usepackage{booktabs}
  \usepackage{amsmath}
  \usepackage{enumitem}
  \usepackage{amssymb}
  \usepackage{textcomp}
% \usepackage{etoolbox}

%% numprint 
\npthousandsep{.}
\npdecimalsign{,}

%% ThesisPUC option
%\tablesmode{figtab} %% [nada, fig, tab ou figtab]
%\abreviationsmode{none} %% [none ou use] %% Default is [use]


%%%
%%% Counters
%%%

%% uncomment and change for other depth values
%% \setcounter{tocdepth}{3}
%% \setcounter{lofdepth}{3}
%% \setcounter{lotdepth}{3}
%% \setcounter{secnumdepth}{3}


%%%
%%% New commands and other global definitions
%%%

\input{defs}

%%%
%%% Misc.
%%%

\usecolour{true}

%%%
%%% Titulos
%%%

\author{Wellington Carlos da Rosa Nascimento}
\authorR{Nascimento, Wellington Carlos da Rosa}

\advisor{Marco Aurélio Cavalcanti Pacheco}{Prof.}
\advisorR{Pacheco, Marco Aurélio Cavalcanti}
% If the advisor's department is different from author's department, uncomment the next line and type the correct name and acronym of advisor's institution.
%\advisorInst{institution name}{acronym}

\coadvisor{Marco Antonio Guimarães Dias}{Prof.}
\coadvisorR{Dias, Marco Antonio Guimarães}
\coadvisorInst{Departamento de Engenharia Elétrica}{PUC-Rio}

%% \title{Desenvolvimento de um sistema de microscopia digital para
%%  classificação automática de tipos de hematita em minério de ferro}

\title{Aplicação de Redes Neurais na Avaliação Econômica de Projetos de E\&P: Uma Abordagem Baseada em Valor da Informação Sequencial e Opções Reais}

\titleuk{Neural Networks Applied to the Economic Evaluation of E\&P Projects: A Sequential Value of Information and Real Options Approach}

%% \subtitulo{Aqui vai o subtitulo caso precise}

\day{07}
\month{Março}
\year{2025}

\city{Rio de Janeiro}
\CDD{620.11}
\department{Engenharia Elétrica}
\program{Engenharia Elétrica}
\school{Centro Técnico Científico}
\university{Pontifícia Universidade Católica do Rio de Janeiro}
\uni{PUC-Rio}

%%%
%%% Jury
%%%

\jury{%
  \jurymember{Pierre-Simon, Marquis de Laplace}{Prof.}
    {University of Caen}{France}
  \jurymember{Andrey Nikolaevich Kolmogorov}{Prof.}
    {Moscow State University}{Russian}
  \jurymember{William Sealy Gosset}{Prof.}
    {New College - Oxford}{England}
  \jurymember{Fischer Sheffey Black}{Prof.}
    {Harvard University}{USA}
}

%%%
%%% Resume
%%%

\resume{%
  Bacharel e Mestre em Física pela Universidade Federal de Alagoas. Trabalha desde de 2010 na Petrobras como Geofísico Senior atuando na Análise Econômica de Projetos Exploratórios.}

%%%
%%% Acknowledgment (REMINDER TO SCHOLARSHIP STUDENTS. Do not forget to thank the agencies that supported your work.)
%%%

\acknowledgment{%
  \noindent I would like to first thank my advisor testando...
  \bigskip

  \noindent Then I wish to thank ...
}

%%%
%%% Catalog prekeywords
%%%

\catalogprekeywords{%
  \catalogprekey{Engenharia Química}%
  \catalogprekey{Engenharia de Materiais}%
}

%%%
%%% Keywords
%%%

\keywords{%
  \key{Minério de Ferro}
  \key{Cristais de Hematita}
  \key{Microscopia Digital}
  \key{Análise de Imagens}
  \key{Classificação}
  \key{Microscopia de Luz Polarizada}
}

\keywordsuk{%
  \key{Iron Ore}%
  \key{Hematite Crystals}%
  \key{Digital Microscopy}%
  \key{Image Analysis}%
  \key{Classification}%
  \key{Polarized Light Microscopy}%
}

%%%
%%% Abstract
%%%

\abstract{%
  O minério de ferro é um material policristalino oriundo de processos
  naturais complexos durante tempos geológicos, que dão origem ...
}

\abstractuk{%
  Iron ore is a polycrystalline material created by complex natural
  processes during geological periods, which give rise to ...}

%%%
%%% Dedication
%%%

\dedication{%
  Aos meu pais, filhos e esposa. A todos os meus familiares.\\
À hipótese de Laplace.
}

%%%
%%% Epigraph
%%%

\epigraph{%
  My beautifull epigraph
}
\epigraphauthor{Wassily Kandinsky}
\epigraphbook{Regards sur le passé}

%%%
%%% Hyphenation
%%%

\hyphenation{PON-TI-FÍ-CIA}

%%%
%%% 
%%%

\begin{document}

  \input{chapter-1}
  \input{chapter-2}
  \input{conclusions}
  %% ...
  \arial
  \bibliography{tiny}
  \normalfont
  \input{appendix}

\end{document}
